---
title: "Test"
author: "Ryo®, Eng Lian Hu"
date: "October 25, 2015"
output: html_document
---

```{r load-packages, include=FALSE}
## You can write as ```{r load-packages, include=FALSE} if you want to hide the particular chunk
## Setting to omitt all warnings
options(warn=-1)

## Loading the packages
if(!'devtools' %in% installed.packages()){
  install.packages('devtools')}
if(!'BBmisc' %in% installed.packages()){
  install.packages('BBmisc')}

suppressPackageStartupMessages(library('BBmisc'))
pkgs <- c('devtools','stringr','stringi','reshape','reshape2','data.table','sparkline','DT','plyr','dplyr','magrittr','foreach','doParallel','rmarkdown','tidyr','gtable','grid','gridExtra','pander','stringdist','knitr','rmarkdown','lubridate','d3Network','networkD3','htmlTable')
suppressAll(lib(pkgs)); rm(pkgs)
```

Testing output of the coding.

```{r setting, include=FALSE}
## Preparing the parallel cluster using the cores
doParallel::registerDoParallel(cores = 16)
#' @BiocParallel::register(MulticoreParam(workers=2))

## Make pretty table
## http://kbroman.org/knitr_knutshell/pages/figs_tables.html
## knitr configuration
opts_knit$set(progress=FALSE)
opts_chunk$set(echo=TRUE, message=FALSE, tidy=TRUE, comment=NA, fig.path="figure/", fig.keep="high", fig.width=10, fig.height=6, fig.align="center")

## Table width setting
panderOptions('table.split.table', Inf)
```

```{r read-datasetA, echo=TRUE, results='asis'}
## Read the datasets
## Refer to **Testing efficiency of coding.Rmd** at chunk `get-data-summary-table-2.1`
source(paste0(getwd(),'/function/readfirmDatasets.R'))
years <- seq(2011,2015)
mbase <- readfirmDatasets(years=years)
dateID <- sort(unique(mbase$datasets$Date))
#'@ pander(head(mbase$datasets)) ## exactly same layout with kable(x)

## example of the dataset from firm A + spbo result in the research paper
##   due to the data heavy and overload ,max 5mb while generated 79mb html file, here I just simply subset the head section

mbase$datasets %>% datatable(.,extensions = 'TableTools', options = list(
    dom = 'T<"clear">lfrtip',
    tableTools = list(sSwfPath=copySWF(pdf=TRUE))
  )
)
```

I just simply refer to <http://rstudio.github.io/DT/extensions.html> and also <http://datatables.net/reference/option/dom>, <https://rstudio.github.io/DT/003-tabletools-buttons.html> and casually wrote the code, the outcome is statisfied but the `TableTools` button **Copy**, **CSV**, **Excel** doesn't work but only **Print**. Any solution?

```{r}
#'@ mbase$datasets %>% datatable(.,extensions=c('ColReorder','ColVis','TableTools'),options=list(dom='CT<"clear">Rlfrtip',colVis=list(exclude=c(0),activate='mouseover'),tableTools=list(sSwfPath=copySWF()),scrollX=TRUE,scrollCollapse=TRUE))

#'@ #'@ mbase$datasets %>% datatable(.,extensions=c('ColReorder','ColVis','TableTools'),options=list(dom='T|C<"clear">R|lfrtip',colVis=list(exclude=c(0),activate='mouseover'),tableTools=list(sSwfPath=copySWF()),scrollX=TRUE,scrollCollapse=TRUE))

#'@ mbase$datasets %>% datatable(.,extensions=c('ColReorder','ColVis','TableTools'),options=list(dom='T|C<"clear">l|Rfrtip',colVis=list(exclude=c(0),activate='mouseover'),tableTools=list(sSwfPath=copySWF()),scrollX=TRUE,scrollCollapse=TRUE))

```

Thanks lot...

```{r read-datasetB, echo=FALSE, results='asis'}
## Load the scraped spbo livescore datasets.
#'@ source(paste0(getwd(),'/function/readSPBO2.R'))
#'@ spboData <- readSPBO2(dateID=dateID, parallel=FALSE)
## example of the scrapped livescore dataset in the research paper
##   due to the data heavy and overload ,max 5mb while generated 79mb html file, here I just simply subset the head section
#'@ spboData %>% head %>% kable(.,caption='table 2.2')
```

```{r matching-01, echo=FALSE, results='asis'}
## Get and filter the teams' name
## Filter and drop the first-half, corners and other games
#'@ teamID <- sort(unique(c(as.character(mbase$datasets$Home), as.character(mbase$datasets$Away))))
#'@ teamID <- teamID[!teamID %in% mbase$others]

#'@ spboTeam <- sort(c(as.vector(spboData$Home), as.vector(spboData$Away)))
#'@ spboTeamID <- sort(unique(spboTeam))

#'@ df1 <- data.frame(team=teamID[tolower(teamID) %in% tolower(spboTeamID)], spbo=spboTeamID[tolower(spboTeamID) %in% tolower(teamID)]) %>% tbl_df %>% mutate(team=as.character(team),spbo=as.character(spbo),pass=ifelse(team==spbo,'Duplicated','Capital Letters')) %>% arrange(pass)
#'@ row.names(df1) <- NULL

#'@ rbind(df1 %>% filter(pass=='Duplicated') %>% head(3),df1 %>% filter(pass=='Capital Letters') %>% head(3)) %>% htmlTable(.,format = "html", output = F, align = c("l", "c", "c", "c"), escape=F,table.attr="class='table table-striped table-hover'")

#'@ rbind(df1 %>% filter(pass=='Duplicated') %>% head(3),df1 %>% filter(pass=='Capital Letters') %>%head(3)) %>% kable(.,caption='table 2.2')
```

```{r matching-05A, echo=FALSE, results='asis'}
#'@ source(paste0(getwd(),'/function/makeList.R'))
## Since the elements are not much enough but list quit a number, just set parallel=FALSE will be faster few minutes.
#'@ dfm <- makeList(mbase, spboData, levDist=0.1, parallel=FALSE)
```

```{r decission-tree-A, echo=FALSE, results='asis'}
## Refered `rpart` and `randomForest` to plot the decision tree, showing how to match the teams' name but required numeric data and also static graph.
## Here I using `d3Network`
#'@ d3data <- dfm$data %>% data.frame
#'@ d3data$X1 <- ifelse(is.na(d3data$X1),'NA',d3data$X1)
#'@ d3data %>% d3SimpleNetwork(.,width='automatic', height=400) ## https://github.com/christophergandrud/d3Network/issues/31
#'@ d3data %>% as.list %>% d3Tree ## https://github.com/christophergandrud/d3Network/issues/31
#'@ d3data[1:2] %>% simpleNetwork(.,width=400, height=400)
```

Since the `simpleNetwork` function only apply to 2 columns dataset, here I split to be 2 graphs.

```{r decission-tree-B, echo=FALSE, results='asis'}
#'@ d3data[3:4] %>% simpleNetwork(.,width='auto', height=800)
```

```{r matching-05B, echo=FALSE, results='asis'}
#'@ datatable(dfm$data)
```

